---
title: "Shiny App for Comparing Stock Price History"
author: "Mohit Gupta"
date: "September 11, 2017"
output: 
  ioslides_presentation: 
    widescreen: yes
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,message = FALSE,warning = FALSE)
```

```{r startup}
library(shiny)
library(plotly) 
library(quantmod)

# Stock symbols that will be used 
symbols <- c("AAPL", "MSFT", "AMZN", "NFLX", "GOOG")
symNames<<- c("Apple","Microsoft", "Amazon", "Netflix", "Google")

# Get price history from yahoo using quantmod and save. Used saved data if available.
if (!file.exists("quantmod_prices.RData")) {
	getSymbols(Symbols = symbols, src="yahoo")
	ds <- data.frame(Date = index(MSFT), AAPL[,6], MSFT[,6], AMZN[,6], NFLX[,6], GOOG[,6])
	names(ds) <- c("Date", symNames)
	save(ds, file="quantmod_prices.RData")
} else {
	load("quantmod_prices.RData")
}

```
## Description
This shiny application allows one to select one or more stocks (out of an available list of 5) and to see their daily closing price history in an interactive fashion.  

If two or more stocks are selected, one can either overlay the price history graphs on top of each other, or stack them vertically as separate graphs.  

An interactive widget on the X-axis allows one to change the start and end dates of the price history shown.  

A "Get Help" button displays a popup with brief help/documentation.

## Tools and Features used  
- quantmod library for fetching selected stock symbol information from Yahoo
- shiny to build the application and interactive content in this presentation
- plotly for the interactive graphs and for the stacked plot (plotly::subplot)
- RMarkdown Slidy to build this presentation
- shinyapps free account to host this presentation
- Possibly gihub to host this interactive presentation (not decided at the time of writing this doc)  

Code is available at this link - `r tags$a(href="http://www.google.com", "Github.")`


## Input Panel of The Application  
Here is a rough **mockup** of what the input panel looks like.  One can choose one or more stocks and choose the graph type and there is a Help button that opens a popup.
```{r input_Panel}
pageWithSidebar(
	headerPanel("Tech Stoch Comparator"),
	sidebarPanel(
		selectInput(inputId="sel_symbols", label="Select One or More Stocks", choices=symNames, multiple=TRUE),
		br(),br(),
		radioButtons("stack_type", label="Stack or Overlay?", 
					 choices=c("Stack","Overlay"), selected="Stack", inline=TRUE),
		br(),
		actionButton("goButton", "Go!"),
		actionButton("help", "Show Help")
	),
	mainPanel(plotlyOutput(NULL))
)



```

## Output  
This is a sample generated using R & plotly code from the app but it does not accept input from the previous slide.  For demo slide deck only.  The date slide at the bottom works.  
```{r output_Panel}

sel_symbols <- c("Google", "Apple")

sub_plots <- lapply(sel_symbols, function(sym) {
	plot_ly(ds, x = ~Date, y=as.formula(paste0("~",sym))) %>%
		add_lines(name = sym) %>% 
		layout(
			title = "Stock Prices",
			xaxis = list(rangeslider = list(type = "date")),
			yaxis = list(title = "Price (Log)")
		)
})
subplot(sub_plots, nrows = length(sub_plots), shareX = TRUE, titleX = FALSE)
p
```

